\documentclass{article}
\usepackage[utf8]{inputenc}

\author{me}

\newcommand{\q}[1]{\vskip0.5em\textbf{#1}}

\begin{document}

  % Please 1) submit "draft" version until 21 April to the organizers, and 2) append the final version to your team description paper
  \title{15th Multi-Agent Programming Contest: All questions answered}

  \maketitle

  \section{Team overview: short answers}

  \subsection{Participants and their background}
  \begin{description}
    \item \q{What was your motivation to participate in the contest?}
    \\ Your answer ...
    \item \q{What is the history of your group? (course project, thesis, $\ldots$)}
    \item \q{What is your field of research? Which work therein is related?}
  \end{description}

  \subsection{Statistics}
  \begin{description}
    \item \q{Did you start your agent team from scratch or did you build on your own or someone else's agents (e.g. from last year)?}
    \item \q{How much time did you invest in the contest (for programming, organizing your group, other)?}
    \item \q{How was the time (roughly) distributed over the months before the contest?}
    \item \q{How many lines of code did you produce for your final agent team?}
    \item \q{How many people were involved?}
    \item \q{When did you start working on your agents?}
  \end{description}

  \subsection{Technology \& Techniques}
  \textbf{Did you make use of agent technology/AOSE methods or tools? What were your experiences?}
  \begin{description}
    \item \q{Agent programming languages and/or frameworks?}
    \item \q{Methodologies (e.g. Prometheus)?}
    \item \q{Notation (e.g. Agent UML)?}
    \item \q{Coordination mechanisms (e.g. protocols, games, \dots)?}
    \item \q{Other (methods/concepts/tools)?}
  \end{description}

  \subsection{Agent system details}
  \begin{description}
    \item \q{How do your agents decide \textbf{what} to do?}
    \item \q{How do your agents decide \textbf{how} to do it?}
    \item \q{How does the team work together? (i.e. coordination, information sharing, ...) How decentralised is your approach?}
    \item \q{Do your agents make use of the following features: Planning, Learning, Organisations, Norms? If so, please elaborate briefly.}
    \item \q{Can your agents change their general behavior during runtime? If so, what triggers the changes?}
    \item \q{Did you have to make changes to the team (e.g. fix critical bugs) during the contest?}
    \item \q{How did you go about debugging your system? What kinds of measures could improve your debugging experience?}
    \item \q{During the contest you were not allowed to watch the matches. How did you understand what your team of agents was doing?}
    \item \q{Did you invest time in making your agents more robust/fault-tolerant? How?}
  \end{description}

  \subsection{Scenario and Strategy}
  \begin{description}
    \item \q{What is the main strategy of your agent team?}
    \item \q{Please explain whether you think you came up with a good strategy or you rather enabled your agents to find the best strategy.}
    \item \q{Did you implement any strategy that tries to interfere with your opponents?}
    \item \q{How do your agents decide which tasks to complete?}
    \item \q{How do your agents coordinate assembling and delivering a structure for a task?}
    \item \q{Which aspect(s) of the scenario did you find particularly challenging?}
  \end{description}

  \subsection{And the moral of it is \ldots}
  \begin{description}
    \item \q{What did you learn from participating in the contest?}
    \item \q{What advice would you give to yourself before the contest/another team wanting to participate in the next?}
    \item \q{What are the strong and weak points of your team?}
    \item \q{Where did you benefit from your chosen programming language, methodology, tools, and algorithms?}
    \item \q{Which problems did you encounter because of your chosen technologies?}
    \item \q{Did you encounter previously unseen problems/bugs during the contest?}
    \item \q{Did playing against other agent teams bring about new insights on your own agents?}
    \item \q{What would you improve (wrt. your agents) if you wanted to participate in the same contest a week from now (or next year)?}
    \item \q{Which aspect of your team cost you the most time?}
    \item \q{What can be improved regarding the contest/scenario for next year?}
    \item \q{Why did your team perform as it did? Why did the other teams perform better/worse than you did?}
    \item \q{If you participated in the ``free-for-all'' event after the contest, did you learn anything new about your agents from that?}
  \end{description}
\end{document}
