\documentclass{article}

\begin{document}
\title{Multi-Agent Programming Contest 2020\\Participation Registration Template}
\author{Author/s, Affiliation/s}
\maketitle

\begin{abstract}
  Please follow the given template structure for your submission. It is vital to explain in this submission how you are using a multi-agent approach (or why not).

  You need to submit the first section (General) of the document as PDF to the mailing list and the complete document to one of the organizers. (Of course you are free to submit the complete document to the mailing list as well).

  \begin{center}
    due \textbf{10 August 2020}
  \end{center}
\end{abstract}


\section*{General}

\begin{enumerate}
  \item What is the name of your team?
  \item Which (agent) platform/programming language(s)/frameworks are you using and why?
  \item Any tips you want to give the other participants? :)
\end{enumerate}

\section*{Specifics}

\subsection*{Organization}

\begin{enumerate}
  \item Who is the main-contact? Please also provide an email address.
  \item The contest is planned for October/November. If possible, please indicate any preferences/constraints you might have regarding the dates.
\end{enumerate}

\subsection*{System Analysis and Design}

\begin{enumerate}
  \item What is the \textbf{main strategy} of the agent team?
  \item Do you use any existing MAS \textbf{methodology}, e.g. Prometheus, O-MaSE, Tropos, \dots?
  \item Do you plan to \textbf{distribute} your agents on several machines?
\end{enumerate}

\subsection*{Agent Development}

\begin{enumerate}
  \item Which \textbf{development} platform and tools (e.g. IDEs) are you using?
  \item If you used agent technology, did you have previous experience?
  \item Do you think your choice of tools/platforms/\dots already paid off?
\end{enumerate}

\subsection*{Evaluation}

\begin{enumerate}
  \item What are strengths of your (agent) team?
  \item What are the (known) weaknesses of your (agent) team?
  \item How far do you think you are with your agents? What are you planning to add/change until the contest?
\end{enumerate}

\end{document}
