\documentclass{article}

\usepackage{hyperref}

\begin{document}
\title{Multi-Agent Programming Contest 2018\\Participation Registration Template}
\author{Author/s, Affiliation/s}
\maketitle

\begin{abstract}
  Please follow the given template structure for your submission. It is vital to explain in this submission how you are using a multiagent approach.

  You need to submit the first section (General) of the document as PDF to the mailing list and the complete document to one of the organizers. (Of course you are free to submit the complete document to the mailing list as well).

  \begin{center}
    due \textbf{12th of August, 2018}
  \end{center}
\end{abstract}


\section*{General}

\subsection*{Introduction}

\begin{enumerate}
  \item What is the name of your team?
  \item Who are the members of your team? Please provide names, academic
    degrees and institutions.
  \item Who is the main-contact? Please also provide an Email address.
  \item How much time (developer hours) will you have invested (approximately)
    until the tournament?
\end{enumerate}

\section*{Specifics}

\subsection*{System Analysis and Design}

\begin{enumerate}
  \item What is the \textbf{main strategy} of the team?
  \item Do you use any existing MAS \textbf{methodology}, e.g. Prometheus, O-MaSE, or Tropos?
  \item Do you plan to \textbf{distribute} your agents on several machines?
  \item Is your solution based on the \textbf{centralisation} of
   coordination/information on a specific agent? Conversely if you
   plan a decentralised solution, which strategy do you plan to use?
  \item Describe the \textbf{communication strategy} in the agent team. Can you
   estimate the communication complexity of your approach?
  \item Describe the team \textbf{coordination strategy} (if any).
  \item How are the following agent features implemented:
   \emph{autonomy}, \emph{proactiveness}, \emph{reactiveness}?
\end{enumerate}

\subsection*{Software Architecture}

\begin{enumerate}
  \item Which \textbf{programming language} do you plan to use to implement the
    multi-agent system? (e.g. 2APL, Jason, Jadex, JIAC, Goal, Java, C++, $\ldots$)
  \item Which \textbf{development} platform and tools are you using?
  \item Which \textbf{runtime} platform and tools are you using?
    (e.g. Jade, AgentScape, simply Java, $\ldots$)
  \item Which \textbf{algorithms} will be used?
\end{enumerate}

\subsection*{Evaluation}

\begin{enumerate}
  \item If you participated before, roughly how much of your agent team could you recycle from last time?
  \item What are strengths of your (agent) team?
  \item What are the weaknesses of your (agent) team?
  \item Do you think your choice of programming language and/or frameworks paid off?
  \item If you used anything MAS-related, please specify what you think the benefits were (regarding implementation effort, outcome, etc.).
\end{enumerate}

Please explain the reasons for your answers.

\end{document}
