\documentclass{article}

\usepackage{hyperref}

\begin{document}
\title{Multi-Agent Programming Contest 2018\\Participation Registration Template}
\author{Author/s, Affiliation/s}
\maketitle

\begin{abstract}
  Please follow the given template structure for your submission. It is vital to explain in this submission how you are using a multiagent approach.

  You need to submit the first section (General) of the document as PDF to the mailing list and the complete document to one of the organizers. (Of course you are free to submit the complete document to the mailing list as well).

  \begin{center}
    due \textbf{1st September 2019} (no extensions)
  \end{center}
\end{abstract}


\section*{General}

\subsection*{Introduction}

\begin{enumerate}
  \item What is the name of your team?
  \item Who are the members of your team? (names, academic degrees and institutions)
  \item Who is the main-contact? Please also provide an email address.
  \item How much time do you think you will have invested until the tournament?
\end{enumerate}

\section*{Specifics}

\subsection*{System Analysis and Design}

\begin{enumerate}
  \item What is the \textbf{main strategy} of the team?
  \item Do you use any existing MAS \textbf{methodology}, e.g. Prometheus, O-MaSE, or Tropos?
  \item Do you plan to \textbf{distribute} your agents on several machines?
  \item Is your solution based on the \textbf{centralisation} of
   coordination/information on a specific agent? Conversely if you
   plan a decentralised solution, which strategy do you plan to use?
  \item Describe the \textbf{communication strategy} of the agent team.
  \item Describe the team \textbf{coordination strategy} (if any).
  \item How are the following agent features implemented:
   \emph{autonomy}, \emph{proactiveness}, \emph{reactiveness}?
\end{enumerate}

\subsection*{Software Architecture}

\begin{enumerate}
  \item Which \textbf{programming language} did you use to implement the
    multi-agent system? (e.g. 2APL, Jason, Jadex, JIAC, Goal, Java, C++, $\ldots$)
  \item Which \textbf{development} platform and tools are you using?
  \item Which \textbf{runtime} platform and tools are you using? (e.g. Jade, AgentScape, simply Java, $\ldots$)
  \item Which \textbf{algorithms} will be used?
\end{enumerate}

\subsection*{Evaluation}

\begin{enumerate}
  \item What are strengths of your (agent) team?
  \item What are the (known) weaknesses of your (agent) team?
  \item Do you think your choice of programming language and/or frameworks paid off?
  \item If you used anything MAS-related, please specify what you think the benefits were (regarding implementation effort, outcome, etc.).
\end{enumerate}

\end{document}
